### 2015-02-02 src/2_Finance.tex
Agregando hipotesis mercado eficiente

@@

>>>>

\section{Technical analysis}

\section{Fundamental analysis}

@@

Efficient Market Hypothesis (EMH) was developed independently by  Paul Samuelson and Eugene Fama in the 1960s.
EMH also known as the random walk theory states that current stock prices fully reflect available information related to its value and there is no way to earn excess profits
\cite{fama1970}. EMH requires that all the participants have rational expectations, and investors reactions be random and follow a normal distribution pattern. Thus, any one can be wrong about the market, but the market is always right as a whole.
There are three common forms of EMH: weak-form efficiency, semi-strong efficiency and strong-form efficiency.

The weak form claims that prices already reflect all past publicly available information. Then strategies based on technical analysis will not be able to produce excess returns. However, the weak form accepts that some forms of fundamental analysis may still provide excess return. Therefore, future prices cannot be predicted based on analysis of historical data. This implies that future prices movements are determined entirely by information not contained in the past prices and participants are unable to systematically profit from market inefficiencies. 
However, many studies have shown a marked tendency for the stock markets to trend over time periods. Various explanations for such large and apparently non-random price movements have been promulgated. Even Fama has accepted price anomalies which do not follow the weak-form efficiency hypothesis \cite{fama+french2008}.

The semi-strong form of the EMH claims that prices instantly change to reflect new public (not private) information such that no excess return can be obtained. In this form neither technical or fundamental analysis can produce excess return.

The strong form of the EMH additionally claims that prices instantly reflect even hidden, private or "insider" information.

EMH is based on rational human behaviour and its validity has been criticised by
psychologists and behavioural economists who argue that the EMH is based
on counterfactual assumptions regarding human behaviour, that is,
rationality. Recent advances in evolutionary psychology and the cognitive
neurosciences may be able to reconcile the EMH with behavioural
anomalies. On the other hand, if the EMH is true, the market really walks randomly and therefore there shouldn't be any difference between experienced and novice traders. Kim Man Lui proved the contrary in a controlled experiment \cite{man2013}.
